Modern Graph Generators: A Survey

### 2018-11-07 generators_GraphDatabases.tex
last pass on my side
Corrections of similarities from iThenticate - part I

\paragraph{gMark}  gMark~\cite{gMark} is a schema-driven, domain-independent and query language-independent graph instance and query workload generator.  It leverages a schema definition,
called a \emph{graph configuration}, which includes the enumeration of predicates (i.e., edge labels) and node types (i.e., node labels) occurring in the data, along with their properties in generated instances (occurrence constraints, degree distribution, etc.). \emph{Query workload configuration}  describes parameters of the queries to be generated (e.g., number of queries, arity, shape, selectivity etc.). The authors prove that given a graph configuration $G$, deciding whether there exists a graph satisfying $G$ is NP-complete. And, that given a query workload configuration $Q$, deciding
whether there exists a query workload satisfying $Q$ is NP-complete. Hence, gMark follows a heuristic strategy in the generation -- it attempts to achieve the exact values of the parameters and it may decide to relax some of them in order to obtain linear running time. gMark generates graphs under the form of N-triples and query workloads in four concrete syntaxes, including Cypher\footnote{\url{https://neo4j.com/developer/cypher-query-language/}}, SPARQL, SQL and LogicQL.

\paragraph{GraphGen}  GraphAware GraphGen\footnote{\url{http://graphgen.graphaware.com/}} is a graph generation engine based on Neo4j's\footnote{\url{https://neo4j.com/}} query language Cypher~\cite{GraphGen}.  It creates nodes and relationships based on a schema definition expressed in Cypher, and it can also generate property values on both
nodes and edges. As such, GraphGen is a precursor of property graphs generators. The resulting graph can be exported to several formats (namely GraphJson\footnote{\url{https://github.com/GraphAlchemist/GraphJSON/wiki/GraphJSON}} and CypherQueries) or loaded directly to a DBMS. However, it is very likely that it is not maintained anymore due to the lack of updates provided.

>>>>

\paragraph{gMark}  gMark~\cite{gMark} is a schema-driven, domain-independent and query language-independent generator generating both graph instances and query workload.  It is based on a  definition of \emph{graph configuration} which involves the list of predicates (i.e., edge labels) and node types (i.e., node labels) occurring in the data together with their further properties such as degree distribution, occurrence constraints, etc. \emph{Query workload configuration}  describes parameters of the queries to be generated (e.g., number of queries, arity, shape, selectivity etc.). The authors prove that deciding whether there exists a graph satisfying a given graph configuration $G$ is NP-complete. And, similarly, deciding
whether there exists a query workload satisfying a given query workload configuration $Q$ is also NP-complete. Hence, gMark generating is based on a heuristic strategy: it tries to achieve the exact values of the given parameters, however, in order to obtain linear running time it may decide to relax some. gMark generates graphs under the form of N-triples and query workloads in four concrete syntaxes, including Cypher\footnote{\url{https://neo4j.com/developer/cypher-query-language/}}, SPARQL, SQL and LogicQL.

\paragraph{GraphGen}  GraphAware GraphGen\footnote{\url{http://graphgen.graphaware.com/}} is a graph generation engine based on Neo4j's\footnote{\url{https://neo4j.com/}} query language Cypher~\cite{GraphGen}.  It creates nodes and relationships based on a schema definition expressed in Cypher, and it can also generate property values on both
nodes and edges. As such, GraphGen is a precursor of property graphs generators. The resulting graph can be exported to several formats (namely GraphJson\footnote{\url{https://github.com/GraphAlchemist/GraphJSON/wiki/GraphJSON}} and CypherQueries) or loaded directly to a DBMS. However, it is very likely that it is not maintained anymore due to the lack of available updates.

### 2018-11-07 generators_SocialNetworks.tex
Corrections of similarities from iThenticate - part I

In general, any analysis of social networks identify their various specific
features~\cite{Chakrabarti:2006:GML:1132952.1132954}. For example, a social
graph has high \emph{clustering coefficient}, i.e. the degree of transitivity of
a graph. Or, its diameter, i.e. the minimum number of hops in which some
fraction (e.g., 90\%) of all connected pairs of nodes can reach each other, is
usually low due to weak ties joining faraway cliques.

>>>>

In general, any analysis of social networks identifies their various specific
features~\cite{Chakrabarti:2006:GML:1132952.1132954}. For example, a social
graph often has high \emph{clustering coefficient}, i.e. the degree of transitivity of
a graph. Or, its diameter, i.e. the longest shortest path amongst some fraction (e.g. 90\%) of all connected nodes, is usually low due to weak ties joining faraway cliques.
